\Title

### 2016-03-20 manuscript/manuscript.tex
Corrections to Bott's method by Val

\citet{bott1960} developed an efficient method to determined the basement
relief of a sedimentary basin from gravity observations.
The method requires data on a regular grid of $N_x \times N_y = N$
observations.
The basement relief is then discretized into an equal grid of $M_x \times
M_y = M$ elements with $M_x = N_x$ and $M_y = N_y$.
Bott's iterative method starts with an initial estimate of the basement relief
$\mathbf{p}^0$ equal to the null vector and updates the estimate using the formula

\begin{equation}
    \mathbf{\Delta p} = \dfrac{\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)}{2\pi G \Delta \rho},
    \label{eq:bott}
\end{equation}

\noindent
in which $G$ is the gravitational constant and $\Delta \rho$ is the basin
density contrast.
The iterative process stops when the inversion residuals
$\mathbf{r} = \mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)$ fall below the assumed noise level
of the data.

@@

\noindent
in which $\mathbf{I}$ is the identity matrix.
In this framework,
Bott's method uses a Bouguer plate approximation of the gravitational effect of
the relief, $d_i = 2\pi G \Delta\rho z_i$.
The derivative of $d_i$ with respect to the parameter $z_i$ is
$2\pi G \Delta \rho$, thus linearizing the Jacobian matrix.
However, the non-linearity of the predicted data $\mathbf{d}(\mathbf{p}^k)$ is
preserved.

We propose that Bott's method can also be formulated as a special case of the
Steepest Descent method (Eq.~\ref{eq:steepest}) by setting the Jacobian matrix to

\begin{equation}
    \mathbf{A} = \dfrac{1}{4 \pi G \Delta \rho}\mathbf{I}.
    \label{eq:bott-steepest}
\end{equation}

\noindent
In practice, both formulations lead to Eq.~\ref{eq:bott}.
One of the advantages of Bott's method over the traditional Gauss-Newton or
Steepest Descent is eliminating the computation and storage of the dense
Jacobian matrix $\mathbf{A}$.
Furthermore, Bott's method also does not require the solution of equation
systems.
However, a disadvantage of Bott's method is that it suffers from instability
\citep{silva2014}.
A common approach to counter this issue is to apply a smoothing filter after
the inversion to the unstable estimate, as in \citet{silva2014}.

>>>>

\citet{bott1960} developed an efficient method to determined the depth of the
basement of a sedimentary basin from gravity observations.
The method requires data on a regular grid of $N_x \times N_y = N$
observations.
The basement relief is then discretized into an equal grid of $M_x \times
M_y = M$ elements with $M_x = N_x$ and $M_y = N_y$.
Bott's iterative method starts with an initial approximation of the basement
depths $\mathbf{p}^0$ equal to the null vector.
The method updates the approximation by calculating a parameter perturbation
vector $\mathbf{\Delta p}^k$ using the formula

\begin{equation}
    \mathbf{\Delta p}^k =
        \dfrac{\mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)}{2\pi G \Delta \rho},
    \label{eq:bott}
\end{equation}

\noindent
in which $G$ is the gravitational constant and $\Delta \rho$ is the
contrast between the density of the sediments and the reference density.
The iterative process stops when the inversion residuals
$\mathbf{r}^k = \mathbf{d}^o - \mathbf{d}(\mathbf{p}^k)$ fall below the assumed noise level
of the data.

@@

\noindent
where $\mathbf{I}$ is the identity matrix.
In this framework,
Bott's method uses a Bouguer plate approximation of the gravitational effect of
the relief, $d_i = 2\pi G \Delta\rho z_i$.
The derivative of $d_i$ with respect to the parameter $z_i$ is
$2\pi G \Delta \rho$, thus linearizing the Jacobian matrix.
However, the non-linearity of the predicted data $\mathbf{d}(\mathbf{p}^k)$ is
preserved.

One of the advantages of Bott's method over the traditional Gauss-Newton or
Steepest Descent is the elimination of the computation and storage of the dense
Jacobian matrix $\mathbf{A}^k$.
Furthermore, Bott's method also does not require the solution of equation
systems.
However, a disadvantage of Bott's method is that it suffers from instability
\citep{silva2014}.
A common approach to counter this issue is to apply a smoothing filter after
the inversion to the unstable estimate, as in \citet{silva2014}.
